### 2020-02-25 ChapterBackground/chapterBackground.tex
Updated: Reformat of RakNet in Background and addition of Replica Manager

\subsection{RakNet}
RakNet is the gaming network library used in the development of the implementation of this project. RakNet uses UDP but also provides a reliability and ordering layer. When messages have the reliable option enabled, RakNet guarantees that UDP packets will arrive at their destination eventually. When messages. When messages have the ordered option enabled, RakNet guarantees that the packets are ordered at the destination. Ordering has the advantage of removing the need to handle out of order packets \cite{RakNetReliability}.

>>>>

\section{RakNet}
RakNet is the gaming network library used in the development of the implementation of this project. Features of RakNet used by this study's implementation will now be described.

\subsection{Reliability and Ordering layer}
RakNet uses UDP but also provides a reliability and ordering layer. When messages have the reliable option enabled, RakNet guarantees that UDP packets will arrive at their destination eventually. When messages. When messages have the ordered option enabled, RakNet guarantees that the packets are ordered at the destination. Ordering has the advantage of removing the need to handle out of order packets \cite{RakNetReliability}.

\subsection{Replica Manager}
RakNet provides a replica manager plugin, which supports the use of replicas and delta-encoding for the updates of their states. Replicas are replicated entities, hosted by one node and replicated on connected nodes. For example, a server is responsible for the updates if a set of entities, the entities are then replicated on all connected clients. This manager handles the broadcast of: existing game entities to new connections, new game entities to existing connections; deleted game entities to existing entities and updates of states of replicated entities \cite{RakNetReplica}.
